Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic

### 2020-05-15 paper/main.tex
commit before starting to write

\title{Bayesian Neural Arithmetic Units -- Leveraging The Complex Plane}
\author{
  Niklas Heim,
  V\'aclav \v Sm\'idl,
  Tom\'a\v s Pevn\'y \\
  Artificial Intelligence Center\\
  Czech Technical University\\
  Prague, CZ 120 00\\
  \texttt{\{niklas.heim, vasek.smidl, tomas.pevny\}@aic.fel.cvut.cz}\\
}

@@

It is known that Neural Networks can approximate functions arbitrarily
well\todo{cite universal approx}.  However, this strength of approximation
often comes at the cost of generalization beyond the training data manifold.
\todo{mention ODEs as use case}

@@

\citet{trask_neural_2018} have demonstrated how severe this problem is even for
the simplest arithmetic operations, such as summing or multiplying two numbers.
In order to increase the power of abstraction of Neural Networks they propose a
\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this
problem \cite{trask_neural_2018} and is capable of learning the arithmetic
addition, subtraction, multiplication, and division
$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However,
the NALU comes with the severe limitation not being able to handle negative
inputs due to the logarithm in the multiplication part of the NALU:

@@

\subsection{Gradient surfaces}%
\label{sub:gradient_surfaces}

>>>>

\title{Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic}
\author{
  Niklas Heim,
  V\'aclav \v Sm\'idl,
  Tom\'a\v s Pevn\'y \\
  Artificial Intelligence Center\\
  Czech Technical University\\
  Prague, CZ 120 00\\
  \texttt{\{niklas.heim, vasek.smidl, tomas.pevny\}@aic.fel.cvut.cz}\\
}

@@

It is known that Neural Networks can approximate functions arbitrarily
well\todo{cite universal approx}.  However, this strength of approximation
often comes at the cost of generalization beyond the training data manifold.
This lack of generalization of traditional network architectures becomes 
The inability to generalize to unseen inputs is an indicator for a lack of
abstraction of the task at hand. The model merely sort of memorized the inputs.
Neural Arithmetic Units aim to

\todo{mention ODEs as use case}

@@

\citet{trask_neural_2018} have demonstrated how severe the extrapolation problem is even for
the simplest arithmetic operations, such as summing or multiplying two numbers.
In order to increase the power of abstraction of Neural Networks they propose a
\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this
problem \cite{trask_neural_2018} and is capable of learning the arithmetic
addition, subtraction, multiplication, and division
$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However,
the NALU comes with the severe limitation not being able to handle negative
inputs due to the logarithm in the multiplication part of the NALU:

@@

\subsection{Gradient surfaces}%
\label{sub:gradient_surfaces}
\begin{figure}
  \centering
  %\includegraphics[width=0.8\linewidth]{../plots/test.pgf}
  \input{../plots/test.tikz.tex}
  \caption{Test}%
  \label{fig:test}
\end{figure}
